Title Goes Here

### 2017-08-17 analysis/paper/paper.Rmd
more on the JAS survey, looking at correlations

correlation of data type and location of sharing

@@

# Methods

# Results

```{r get-data, eval = FALSE}
# Note the path that we need to use to access our data files when rendering this document
my_data <- readr::read_csv("../data/raw_data/my_csv_file.csv")
```

# Discussion

# Conclusion

# Acknowledgements

# References

### Colophon

This report was generated on `r Sys.time()` using the following computational environment and dependencies:

```{r colophon, cache = FALSE}
# which R packages and versions?
devtools::session_info()
```

The current Git commit details are:

```{r}
# what commit is this file at? You may need to change the path value
# if your Rmd is not in analysis/paper/
git2r::repository("../..")
```

>>>>

```{r eval=TRUE, fig.cap="No relationship between data file type and data sharing location"}
# correlation of data type and location of sharing
file_type_location <- 
jas_article_survey %>% 
  mutate(file = strsplit(as.character(`What file format?`), ",")) %>% 
  unnest(file) %>% 
  filter(file != "na" & `Where is the data?` != "na") %>% 
  select(file,  `Where is the data?`) %>% 
  mutate(location = case_when(
    grepl("sup", tolower(`Where is the data?`)) ~ "Supplementary",
    grepl("tab", tolower(`Where is the data?`)) ~ "Table",
    grepl("www|dryad|osf", tolower(`Where is the data?`)) ~ "Repository",
  )) %>% 
  mutate(file = case_when(
    grepl("DOCX|doc", file) ~ "DOCX",
    grepl("XLSX| XLSX", file) ~ "XLSX",
    TRUE ~ file
    ))

file_type_location %>% 
  group_by(file, location) %>% 
  tally() %>% 
  ggplot(aes(file, location)) + 
  geom_point(aes(size = n),
             colour = "grey80") +
  theme_bw() + 
  xlab("") + 
  ylab("") +
  scale_size_continuous(range=c(5,25)) + 
  geom_text(aes(label = n)) +
  theme(legend.position = "none") 
```

```{r eval=TRUE, fig.cap="Plot of the relationship between data type and location where it is shared."}
# correlation of data type and location of sharing
data_type_location <- 
jas_article_survey %>% 
  filter(`data type?` != "na" & `Where is the data?` != "na") %>% 
  select(`data type?`, `Where is the data?`) %>% 
  mutate(data_type = case_when(
    grepl("comp", tolower(`data type?`)) ~ "Compositional",
    grepl("c14|osl", tolower(`data type?`)) ~ "Dating",
    grepl("dna", tolower(`data type?`)) ~ "DNA",
    TRUE ~ `data type?`
  )) %>% 
   mutate(location = case_when(
    grepl("sup", tolower(`Where is the data?`)) ~ "Supplementary",
    grepl("tab", tolower(`Where is the data?`)) ~ "Table",
    grepl("www|dryad|osf", tolower(`Where is the data?`)) ~ "Repository"
  ))

data_type_location %>% 
  group_by(data_type, location) %>% 
  tally() %>% 
  filter(n >= 2) %>% 
  ggplot(aes(data_type, location)) + 
  geom_point(aes(size = n),
             colour = "grey80") +
  theme_bw() + 
  xlab("") + 
  ylab("") +
  scale_size_continuous(range=c(5,25)) + 
  geom_text(aes(label = n)) +
  theme(legend.position = "none") 
```

@@
